\begin{thebibliography}{99} % Bibliography - this is intentionally simple in this template

\bibitem{Nat2016}
Energieonderzoek Centrum Nederland. ''Nationale Energieverkenning 2016''

\bibitem{Tande2003}
J. O. G. Tande. "Grid integration of wind farms," in Wind Energy, 2003

\bibitem{Zalkind2016}
D. S. Zalkind and L. Y. Pao. "The fatigue loading effects of yaw control for wind plants," in American Control Conference (ACC), 2016
 
\bibitem{Fleming2014}
P. A. Fleming, P. M. Gebraad, S. Lee, J. W. van Wingerden, K. Johnson, M. Churchfield, P. Moriarty. ''Evaluating techniques for redirecting turbine wakes using SOWFA.'' in Renewable Energy, 2014

\bibitem{Hansen2014}
A. D. Hansen, P. Sørensen, F. Iov, F. Blaabjerg. ''Centralised power control of wind farm with doubly fed induction generators.'' in Renewable Energy, 2005

\bibitem{Boersma2017} 
S. Boersma, B. M. Doekemeijer, P. M. O. Gebraad, P. A. Fleming, J. Annoni,
A. K. Scholbrock, J. A. Frederik, and J-W. van Wingerden. ''A Tutorial on Control-Oriented Modeling and Control of Wind Farms,''
prsented at the American Control Conference, 2017


\bibitem{Kanev2017} 
S. K. Kanev and F. J. Savenije. "Active wake control: loads trends," in Wind Energy, 2017

\bibitem{Wilson2017}
B. Wilson. "Wind Farm Control: Robust Multi-Objective Optimization of a Wind Farm for Different Control Strategies," Unpublished Master's Thesis, 2017

\bibitem{Dijk2016}
M. T. van Dijk, J. W. van Wingerden, T. Ashuri, Y. Li, and M. A. Rotea. "Yaw-Misalignment and its Impact on Wind Turbine Loads and Wind Farm Power Output," in Journal of Physics: Conference Series, 2016

\bibitem{Bastankhah2016}
M. Bastankhah and F. Porte-Agel. "Experimental and theoretical study of wind turbine wakes in yawed conditions," in Journal of Fluid Mechanics, 2016

\bibitem{Gebraad2016}
P. M. O. Gebraad, F. W. Teeuwisse, J. W. Wingerden, P. A. Fleming, S. D. Ruben, J. R. Marden and L. Y. Pao. "Wind plant power optimization through yaw control using a parametric model for wake effects-a CFD simulation study," in Wind Energy, 2016

\bibitem{Jonkman2005}
J. M. Jonkman and M. L. Buhl Jr. "FAST User's Guide,'' National Renewable Energy Laboratory, Golden, CO, Technical Report No. NREL/EL-500-38230, 2005

\bibitem{Firtin2011}
E. Firtin, O. Guler, and S. A. Akdag. "Investigation of wind shear coefficients and their effect on electrical energy generation," in Applied Energy, 2011

\bibitem{Chougule2016}
A. Chougule, S. T. Kandukuri, and H.-G. Beyer. "Assessment of synthetic winds through spectral modeling and validation using FAST." Journal of Physics: Conference Series. Vol. 753. No. 4. IOP Publishing, 2016

\bibitem{Marden2013}
J. R. Marden, D. R. Shalom, and L. Y. Pao. "A model-free approach to wind farm control using game theoretic methods." IEEE Transactions on Control Systems Technology 21.4 (2013): 1207-1214	


\bibitem{vanDijk2016}
M. van Dijk. ''A Study on Yaw-Misaligment: Combined Optimization of Wind Farm Power Production and Structural Loading,'' Unpublished Master's Thesis, 2016

\bibitem{EWEA2016}
EWEA. ''Wind in power, 2015 European statistics,'' 2016

\bibitem{Jonkman2009}
J. M. Jonkman, S. Butterfield, W. Musial, and G. Scott. "Definition of a 5-MW Reference	Wind Turbine for Offshore System Development," National Renewable Energy Laboratory, 2009










\end{thebibliography}